\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
%\usepackage[sfdefault]{noto}

\setlength{\multicolsep}{3.0pt}
\setlength{\columnsep}{5pt}

% Adjust footer
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{5pt} % Increase footskip to resolve fancyhdr warning

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
	\textbf{\Huge \scshape Ajmal Basheer} \\ \vspace{1pt}
	\small{
		\raisebox{-0.1\height}\faPhone\ \href{tel:+919496444520}{\underline{+91 9496444520}} $|$ 
		\raisebox{-0.2\height}\faEnvelope\ \href{mailto:ajmalbuv@gmail.com}{\underline{ajmalbuv@gmail.com}} $|$ 
		\raisebox{-0.2\height}\faLinkedin\ \href{https://linkedin.com/in/ajmalbuv}{\underline{linkedin.com/in/ajmalbuv}} $|$
		\raisebox{-0.2\height}\faGithub\ \href{https://github.com/ajmalbuv}{\underline{github.com/ajmalbuv}}
	}
\end{center}

\section{Summary}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
			Highly motivated Computer Applications student with hands-on experience in full-stack development. Proficient in Python, Django, and PostgreSQL with a strong foundation in building educational management systems. Passionate about creating efficient, user-friendly solutions that improve administrative processes in educational institutions.
	}}
\end{itemize}
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Krupanidhi Degree College}{Bengaluru, Karnataka}
    {Bachelor of Computer Applications}{Aug. 2021 -- July 2024}
  \resumeSubheading
    {MIC Higher Secondary School}{Malappuram, Kerala}
    {Commerce}{June 2017 -- March 2019}
%  \resumeSubheading {International Indian School Dammam}{Dammam, Saudi Arabia}{CBSE}{March 2017}
\resumeSubHeadingListEnd

\section{Relevant Coursework}
\begin{itemize}[leftmargin=*,nosep]
    \begin{multicols}{4}
        \item Computer Networks
        \item Operating Systems
        \item Database Management% Systems
        \item Web Development
        \item Data Structures% and Algorithms
        \item Cyber Security
        \item Software Engineering
        \item Cloud Computing
    \end{multicols}
\end{itemize}

\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {WIMD Technologies Pvt Ltd}{May 2024 -- June 2024}
    {Software Engineer Intern}{Bengaluru, Karnataka}
    \resumeItemListStart
      \resumeItem{Completed a full-time, ten-day internship with \textbf{WIMD Technologies Pvt Ltd}, immersing in real-world scenarios and working on industry-standard tools to complement my academic learning.}
      \resumeItem{\textbf{Developed and Optimized APIs:} Successfully created RESTful APIs using Node.js, implementing secure authentication (JWT) and role-based authorization for data integration between applications, ensuring adherence to industry best practices.}
      \resumeItem{\textbf{Database Design and Performance:} Assisted in designing, maintaining, and optimizing MongoDB databases, including schema creation and indexing, which enhanced data retrieval speed and ensured high performance for large datasets.}
      \resumeItem{\textbf{API Testing and Quality Assurance:} Utilized Postman to develop and execute automated test scripts, identifying and troubleshooting issues across GET, POST, PUT, and DELETE requests, ensuring reliable API performance.}
      \resumeItem{\textbf{Collaborative Problem Solving:} Engaged in team-based debugging and code review sessions, leveraging critical thinking and communication skills to resolve database connectivity and API integration challenges efficiently.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{\href{https://github.com/ajmalbuv/EduManage}{EduManage}} $|$ \emph{Python, Django, PostgreSQL, Docker}}{July 2024}
    \resumeItemListStart
      \resumeItem{\textbf{Developed and Deployed Django Web App:} Built a robust educational management system using Django, implementing dynamic functionality to support educational workflows, enhancing user experience for academic institutions.}
      \resumeItem{\textbf{Multi-Platform Deployment:} Successfully deployed the application on an Ubuntu VPS using Gunicorn, Certbot for SSL, and DuckDNS for DNS management, as well as on Vercel with serverless functions, ensuring high availability and reliability across platforms.}
      \resumeItem{\textbf{Database Management with PostgreSQL:} Configured and managed PostgreSQL as the primary database, optimizing queries and data handling to ensure rapid response times and data integrity within the application.}
      \resumeItem{\textbf{Scalable and Secure Setup:} Employed SSL encryption with Certbot and DuckDNS, securing user data and ensuring compliance with best practices for web application security, while providing scalability with serverless deployment on Vercel.}
      \resumeItem{\textbf{Source Control and Collaboration:} Utilized GitHub for version control and code collaboration, streamlining development workflows, issue tracking, and documentation, facilitating efficient project management and future development.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   \textbf{Languages}{: Python, Java, C, SQL, JavaScript, HTML/CSS, PHP, R} \\
   \textbf{Frameworks}{: React, Node.js, Flask, Django, } \\
   \textbf{Tools}{: GitHub, Docker, Oracle Cloud, Visual Studio, PyCharm, IntelliJ, Postman} \\
   \textbf{Libraries}{: Django Rest Framework (DRF), Mongoose, Express.js, psycopg2, JWT, pandas, NumPy, Matplotlib}
  }}
\end{itemize}

\end{document}